Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-21 paper/paper.tex
Reorder the figures in Section 5

\section{Toward Decidability of Type Conversion and $\eta$ laws}
\label{sec:extension}
\begin{figure}[h]
  \[
    \begin{array}{lcl}
      % \beta\text{-}\mathit{neutral\ terms}\\
      [[e]] & ::= & [[i]]\ |\ [[e f]]\ |\ [[J e f f f]]\ |\ [[if e f
                    f]] \\ \\
      % \beta\text{-}\mathit{normal\ terms} \\
      [[f]] & ::= & [[e]]\ |\ [[Set i]]\ |\ [[Void]]\ |\ [[Pi f f]]\
                    |\ [[f ~ f : f]]\\
            & |   & [[\ f]]\ |\ [[refl]]\ |\ [[Bool]]\ |\ [[true]]\ |\ [[false]]
    \end{array}
  \]
  \caption{$\beta$-neutral and normal forms}
  \label{fig:nenf}
\end{figure}
\begin{figure}[h]
  \drules[I]{$[[Interp I i A S]]$}{Logical Relation}{Ne, VoidNew, BoolNew, EqNew}
  \caption{Extended logical relation}
  \label{fig:logrelopen}
\end{figure}

\scw{Put this introduction before the figure in the section.}
In this section, we sketch out how the logical relation from
Section~\ref{sec:logreldep} can be extended show the existence of
$\beta\eta$ normal forms for (open and closed) well-typed terms. We
first extend parallel reduction to include $\eta$ reduction for
functions.
\begin{center}
  \drule[width=2.5in]{P-AbsEta}
\end{center}
\scw{What happened to the domain type in the $\lambda$ expression? This is
not your syntax...}
\Rref{P-AbsEta} effectively adds $\eta$ laws for functions to our
equational theory since coherence, the untyped relation used for type
conversion, is built on top of parallel reduction. We can recover the
same confluence result about parallel reduction using the standard
techniques from \citet{barendregt:lambda-calculi-with-types,
takahashi-parallel-reduction}, though specifically for the de Bruijn
representation, we need the following anti-renaming lemma about
parallel reduction.
\begin{lemma}[Par anti-renaming]
  \label{lemma:parantirenaming} If $[[a < xi > => b0]]$, then there
exists some $[[b]]$ such that $[[b < xi > = b0]]$ and $[[a => b]]$.
\end{lemma}

@@

>>>>

\section{Toward Decidability of Type Conversion and $\eta$ laws}
\label{sec:extension}
In this section, we sketch out how the logical relation from
Section~\ref{sec:logreldep} can be extended show the existence of
$\beta\eta$ normal forms for (open and closed) well-typed terms. We
first extend parallel reduction to include $\eta$ reduction for
functions.
\begin{center}
  \drule[width=2.5in]{P-AbsEta}
\end{center}

\Rref{P-AbsEta} effectively adds $\eta$ laws for functions to our
equational theory since coherence, the untyped relation used for type
conversion, is built on top of parallel reduction. We can recover the
same confluence result about parallel reduction using the standard
techniques from \citet{barendregt:lambda-calculi-with-types,
takahashi-parallel-reduction}, though specifically for the de Bruijn
representation, we need the following anti-renaming lemma about
parallel reduction.
\begin{lemma}[Par anti-renaming]
  \label{lemma:parantirenaming} If $[[a < xi > => b0]]$, then there
exists some $[[b]]$ such that $[[b < xi > = b0]]$ and $[[a => b]]$.
\end{lemma}

\begin{figure}[h]
  \[
    \begin{array}{lcl}
      % \beta\text{-}\mathit{neutral\ terms}\\
      [[e]] & ::= & [[i]]\ |\ [[e f]]\ |\ [[J e f f f]]\ |\ [[if e f
                    f]] \\ \\
      % \beta\text{-}\mathit{normal\ terms} \\
      [[f]] & ::= & [[e]]\ |\ [[Set i]]\ |\ [[Void]]\ |\ [[Pi f f]]\
                    |\ [[f ~ f : f]]\\
            & |   & [[\ f]]\ |\ [[refl]]\ |\ [[Bool]]\ |\ [[true]]\ |\ [[false]]
    \end{array}
  \]
  \caption{$\beta$-neutral and normal forms}
  \label{fig:nenf}
\end{figure}

@@

\begin{figure}[h]
  \drules[I]{$[[Interp I i A S]]$}{Logical Relation}{Ne, VoidNew, BoolNew, EqNew}
  \caption{Extended logical relation}
  \label{fig:logrelopen}
\end{figure}
